\papertitle

### 2021-03-10 source_separation/paper/paper.tex
Add short introductive text to separation methods

		\subsection{Separation Methods}

			\subsubsection{Non-negative Matrix Factorization} 
			Non-negative matrix factorization \cite{Cichocki_NMF} \cite{Fevotte_NMF} is an \`a priori method, which takes an input non-negative matrix, in this case a spectrogram $S$, in $\mathbb{R} ^{N\times M}$ and decomposes it into a basis matrix $A$ in $\mathbb{R}^{N\times J}$ and a component matrix $X$ in $\mathbb{R}^{J\times M}$ such that $S\approx A\times X$. We use the coordinate descent algorithm from the scikit-learn Python package based on \cite{Cichocki_NMF} with $J$ set to $4$, which selects for 4 features in the dataset. We then output 4 mono waveforms containing each isolated feature $F_i$, where $F_i=A_i\times X_i$ for $i = 1, 2, 3$, or $4$.

@@

			\subsubsection{Universal Sound Separation ConvTasNet}
			This version of ConvTasNet, called TDCN++, was improved by \cite{tdcnpp} in order to be used for general sound separation, and not only for speech. The main architecture remains the same as in \cite{tdcn}, and the changes only affected the masking network. More specifically, feature-wise normalization replaces global normalization, residual connection ranges are extended to improve the flow of information, and learnable scale parameters are introduced to weight the outputs of each residual layer. Those modifications help the model to better extract features without drastically increasing its size.

>>>>

		\subsection{Separation Methods}
	We consider source separation models trained to tackle two distinct separation problems. The first is music source separation (Open-Unmix, Demucs, ConvTasnet). For these architectures, we used models that were pre-trained on the MUSDB18 dataset~\cite{MUSDB18}. Thus, these models outputs four stereo tracks, that correspond to broad instrumental categories defined in the SiSEC 2018 Mus evaluation campaign~\cite{Stoter_SiSEC}, i.e. \textit{vocals, drums, bass} and \textit{other}. The audio sources we consider in this work are often non-musical, but we hope that these source separation methods can still improve the orchestration by separating other types of sound in a musically meaningful way.
	The second one is universal sound separation (TDCN++, NMF), which \cite{tdcnpp} defines as "separating mixtures of arbitrary sounds of different types". 
			\subsubsection{Non-negative Matrix Factorization} 
			Non-negative matrix factorization \cite{Cichocki_NMF} \cite{Fevotte_NMF} is an \`a priori method, which takes an input non-negative matrix, in this case a spectrogram $S$, in $\mathbb{R} ^{N\times M}$ and decomposes it into a basis matrix $A$ in $\mathbb{R}^{N\times J}$ and a component matrix $X$ in $\mathbb{R}^{J\times M}$ such that $S\approx A\times X$. We use the coordinate descent algorithm from the scikit-learn Python package based on \cite{Cichocki_NMF} with $J$ set to $4$, which selects for 4 features in the dataset. We then output 4 mono waveforms containing each isolated feature $F_i$, where $F_i=A_i\times X_i$ for $i = 1, 2, 3$, or $4$.

@@

			\subsubsection{Universal Sound Separation ConvTasNet}
			This version of ConvTasNet, called TDCN++, was improved by \cite{tdcnpp} in order to be used for general sound separation, and not only for speech. The main architecture remains the same as in \cite{tdcn}, and the changes only affected the masking network. More specifically, feature-wise normalizatio	n replaces global normalization, residual connection ranges are extended to improve the flow of information, and learnable scale parameters are introduced to weight the outputs of each residual layer. Those modifications help the model to better extract features without drastically increasing its size.
